sWGS QC

### 2019-11-05 sWGS QC.Rmd
...

dir1 = '~/Data/Ellie/Analysis/multipcf_perPatient/'
dir2 = '~/Data/Ellie/Analysis/validation//'

@@

res.variance = do.call(bind_rows, lapply(list.files(dir1, 'residuals', recursive = T, full.names = T), function(f) {
  read_tsv(f, col_types = 'ccdddddl')
}))

@@

```{r, echo=F}
res.variance %>% filter( round(varMAD_median,3) > cutoff ) %>% select(patient,sample, varMAD_median) %>% kable(caption=paste0('Samples variance > ',cutoff)) %>% kable_styling('striped')

@@

```{r, echo=F}
val.file = '~/Data/BarrettsProgressionRisk/QDNAseq/validation/sWGS_validation_batches.xlsx'
sheets = readxl::excel_sheets(val.file)[1:4]
all.val = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s) %>% select(`Hospital Research ID`, matches('Status'), `Block ID`,`Sample Type`, `SLX-ID`, `Index Sequence`, Cohort, Batch, RA, matches('Collection')) %>% dplyr::filter(!is.na(`SLX-ID`) & RA == 'C.Kosmidou') %>% mutate_at(vars(`SLX-ID`, `Block ID`), list(as.character)) 
}))
all.val = all.val %>% select(-Collection)

@@

resVal = do.call(bind_rows, lapply(list.files(dir2, 'residuals', recursive = T, full.names = T), function(f) {
  readr::read_tsv(f, col_types = 'cdddddl', col_names = F) %>% set_names('sample', 'varMAD_median', 'varMAD_sd', 'varMAD_Q1', 'varMAD_Q3', 'n.segs', 'Pass') %>%  
    mutate(`Patient ID` = as.character(basename(dirname(f))))
})) %>% select(`Patient ID`, sample, matches('varMad'), n.segs, Pass)

resVal = resVal %>% filter(sample %in% all.val$Sample)

>>>>

dir1 = '~/Data/BarrettsProgressionRisk/Analysis/pcf_perPatient/50kb/'
dir2 = '~/Data/BarrettsProgressionRisk/Analysis/validation/pcf_perPatient/50kb/'

@@

res.variance = do.call(bind_rows, lapply(list.files(dir1, 'residuals', recursive = T, full.names = T), function(f) {
  read_tsv(f, col_types = 'ccddddl')
}))

@@

```{r, echo=F}
res.variance %>% filter( round(varMAD_median,3) > cutoff ) %>% dplyr::select(patient,samplename,varMAD_median) %>% 
  kable(caption=paste0('Samples variance > ',cutoff)) %>% kable_styling('striped')

@@

```{r, echo=F}
val.file = '~/Data/BarrettsProgressionRisk/QDNAseq/validation/sWGS_validation_batches.xlsx'
sheets = readxl::excel_sheets(val.file)[1:4]
all.val = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s) %>% dplyr::select(`Hospital Research ID`, matches('Status'), `Block ID`,`Sample Type`, `SLX-ID`, `Index Sequence`, Cohort, Batch, RA, matches('Collection')) %>% 
    dplyr::filter(!is.na(`SLX-ID`) & RA == 'C.Kosmidou') %>% 
    mutate_at(vars(`SLX-ID`, `Block ID`), list(as.character)) 
}))
all.val = all.val %>% dplyr::select(-Collection)

@@

resVal = do.call(bind_rows, lapply(list.files(dir2, 'residuals', recursive = T, full.names = T), function(f) {
  readr::read_tsv(f, col_types = 'ccddddl') #%>% set_names('sample', 'varMAD_median', 'varMAD_sd', 'varMAD_Q1', 'varMAD_Q3', 'n.segs', 'Pass') %>%  
   # mutate(`Patient ID` = as.character(basename(dirname(f))))
})) %>% dplyr::select(patient, samplename, matches('varMad'), Pass)

resVal = resVal %>% filter(samplename %in% all.val$Sample)
